\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-06-06 eg6-letters/NIM/author_list.tex
Add Eric et Yohann to authors

\author{R.~Dupr\'e}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{M.~Hattawy}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{N.~Baltzell}  \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{A.~Celentano} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{K.~Hafidi}    \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}

%\author{} \affiliation{}
%

>>>>

\author{R.~Dupr\'e}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{M.~Hattawy}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{N.~Baltzell}  \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{A.~Celentano} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
\author{K.~Hafidi}    \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
\author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
\author {E.~Voutier} \affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
%\author{} \affiliation{}
%
